\bf Range Analysis for the IonMonkey JavaScript engine

### 2012-04-29 project-writings/paper.tex
More things

We have implemented integer value range analysis in the IonMonkey
engine and used it to eliminate provably unnecessary overflow checks.

>>>>

We have implemented integer value range analysis in the IonMonkey
engine and used it to eliminate provably unnecessary overflow checks.
We implemented an SSA-based worklist range analysis algorithm that
propagates integer ranges for variables by performing range
arithmetic. The algorithm is based off of Gough and Klaeren's range
analysis for bounds check elimination
\cite{Gough94eliminatingrange}. A range (including information about
possible overflow) is associated with each computation, and the ranges
are consulted to determine whether to perform overflow checks for
arithmetic computations.

OTHER OPTIMIZATIONS WE DO

OUR CONTRIBUTIONS
